---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

This page is about making some plotly examples. 

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

Let's look at the NYC airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  select(neighbourhood_group, neighbourhood, stars, price, room_type, lat, long) %>% 
  filter(neighbourhood_group == "Manhattan", 
         room_type == "Entire home/apt", 
         price %in% 100:500) %>% 
  drop_na(stars)
```

## Make a scatterplot 

Here's a plotly scatterplot! 

```{r}
nyc_airbnb %>% 
  mutate(
    text_label = str_c("Price: $", price, "\nStars: ", stars)
  ) %>% 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers", text = ~ text_label, color= ~price, alpha = 0.5
  )
```

str_c() = concatenate string variable 

## Plotly boxplot 

```{r}
nyc_airbnb %>% 
  mutate(
    neighbourhood = fct_reorder(neighbourhood, price)
  ) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```

Puts the x axis in the order of whatever factor variable exists; if no order is specified, then it does alphabetical order. 

Also, if you're looking at the neighborhoods, click once and you remove that one; click twice and look only at that one, etc. 

Here comes a bar chart...

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```

When plotly wants to make a bar chart, you say the x axis and then how tall you want the bar to be by N. 

You can make more complicated plots - Google plotly R --> quick start examples, basic charts

Lots of cool examples; Lots of charts (Gantt Chart)

## ggplotly

People like this - make something in ggplot and then ggplotly to make it a plotly from a ggplot 

```{r}
gg_lat_long = 
  nyc_airbnb %>% 
  ggplot(aes(x = lat, y = long, color = price)) + 
  geom_point()

ggplotly(gg_lat_long)
```

## What kinds of stuff can you put in our dashbaords 

Make the dashboard RMD - can look at extra links on the course website and you can see the underlying data from the website he has references 

## WHY did we put the dashboard in a separate place (on the dashboard) 

If it's in the normal folder, it renders to the normal website, which is a problem because it doesn't work as a dashboard. 

How to fix this: 
1) Build your website
2) Command line version of this 

